Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-23 ASA2013/asa2013.tex
la2pdf commit - 2013:01:23	03:10:38	(Wed23.Jan)

The beamspace MVDR formulation very closely resembles that of time domain MVDR. The main difference is the initial need to Fourier transform the data:
\begin{gather}
\x_\text{BS}[n] = \B\x[n], \qquad \B\in \mathbb{C}^{N_b,M}, \qquad \text{where} \qquad [\B]_{p,q} = \frac{1}{\sqrt{M}} e^{-j2\pi\,p\,q/M}.\label{beamspace}
\end{gather}
The number of angles to compute is here defined by $N_b$, $\B$, usually referred to as a Butler matrix
Complexity: To frequency domain: O($N_b\,L$). Build $R_\text{BS}$, O($N_b^2\,N_L\,N_K$), Inversion: O($N_b^3$).

>>>>

The beamspace MVDR formulation very closely resembles that of time domain MVDR. The main difference is the initial need to Fourier transform the data:
\begin{gather}
\x_{\text{BS},l}[n] = \B\x_l[n], \qquad \B\in \mathbb{C}^{N_b,M}, \qquad \text{where} \qquad [\B]_{p,q} = \frac{1}{\sqrt{M}} e^{-j2\pi\,p\,q/M}.\label{beamspace}
\end{gather}
Here $\B$ is referred to as the Butler matrix, $l$ is the subarray index, and $N_b$ is the number of beams that should be computed. Note has once $\x_{\text{BS},l}[n]$ is computed, $\eR_\text{BS}$ can be found as in (\ref{spatialR}), $\w_\text{BS}$ as in (\ref{weights}), and $z$ as in (\ref{z}).

By reducing the covariance size from $L$ to $N_b$ we also reduce the estimation step to O($N_K N_L N_b^2$), and the inversion step to O($N_b^3$). The downside is the additional O[$N_b  Complexity: To\,L$) computations required  frequency domain: O($N_b\,L$). Build $R_\text{BS}$, O($N_b^2\,N_L\,N_K$), Inversion: O($N_b^3$).
